A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-05-20 manuscript.Rmd
Final changes

<!-- define replicability and then... 
 define reproducibility -->
Even worse, researchers might often not even be able to achieve reproducibility---defined as the ability to obtain identical results from the *same* data with the *same* computer code.
Over the past decades, computational statistical methods have radically changed the ability of researchers from all disciplines to process and analyze data with complex statistical models.
With these advances came challenges that contribute to broader concerns of irreproducibility in the published literature, among them the lack of exact and unambiguous documentation of computational methods and each computational step taken.
With computationally intensive data analyses, access to the steps taken to process data and generate findings is as important as access to the data themselves [@vanlissa2020worcs].
Only with access to both data and procedures can we guarantee full computational reproducibility, meaning that the creations emanating from a given data analysis (a statistical result or an entire manuscript describing the results) can be exactly reproduced at any time in the future, by any person, and on any computer. <!-- CJ this final claim is questionable, at least before introducing the concept of containerization. Just using data and procedures, you cannot guarantee reproducibility on any computer.-->

In fact, the research community has long accepted reproducibility as an important element of "good scientific practice." <!-- examples missing -->
However, ensuring reproducibility of computational analyses is still tedious and difficult, and there are still no widely accepted standards that can guide researchers when setting up their data analyses.
Even though transparency has increased across scholarly disciplines (that is, data and methods are increasingly openly shared), most of these open repositories do not provide sufficient information to reproduce relevant computational and statistical results.
For example, @hardwicke2018 attempted to replicate studies ostensibly adhering to the standards of open science in the journal Cognition.<!-- CJ How do you replicate open materials? At least in the social sciences "open materials" is taken to mean that you have used a permissive license on a newly developed questionnaire or other research material. -->
Out of 35 published articles, results of 22 articles could be reproduced but in 11 of these cases, assistance from the original authors was required.
For 13 articles, at least one outcome could not be reproduced —-- even with the original authors' assistance.
@obels2020 showed that in 62 Registered Reports, 41 had data available, and 37 had analysis scripts available.
The authors could execute only 31 of the scripts without error and were able to reproduce the results of only 21 articles (within a reasonable period of time).
Thus, there is a dire need to establish standards for reproducible workflows for scientific rigor.<!-- CJ It does not automatically follow that the problem you describe necessitates reproducible workflows. I would procede as follows: 1) use this example to conclude the existence of a problem (even "open" studies do not reproduce), 2) present workflows as a solution. -->

From our personal experience,<!--CJ This undermines the credibility of the argument. This is not an opinion piece--> the lack of a proper incentive structure and the dreary perspective of having to spend several extra hours if not days to properly set of a code repository to become reproducible, makes many scholars skip this extra step. <!-- CJ I am not sure this is the primary reason. Indeed, incentives are important - but in that context, perhaps reference DORA? I think you were just on a good track, arguing that even with the best intentions, researchers often fail to make their work reproducible. Your workflow will ensure that their next attempt is succesful.-->
If reproduction would require merely minutes instead of hours,<!-- CJ Now we're back to ease-of-use, not incentives.-->
it could greatly facilitate collaboration within and across research projects. <!-- CJ This is a different, third argument: In order to collaborate effectively, researchers should be looking at exactly the same data, code and results. I suggest to organize these arguments, and address them each exhaustively in turn. --> 
<!-- Guiding principle: spending machine compute time instead of human research time -->
To achieve this boost in productivity, we must place the burden of reproducibility upon computers instead of the researchers.<!-- CJ I understand what you mean, but it's not yet communicated effectively because you have not yet made explicit that reproducible projects will indeed facilitate collaboration, and increase opportunities for collaboration (e.g., with strangers through github), and will therefore lead to a boost in productivity. Also - ask yourself if this boost in productivity is convincing to individual researchers, your target audience. It seems like this would be more convincing to management and policy makers.-->
To this end, we demand <!-- CJ It's you creating the product, so.. you demand this of yourself? Or do you mean that you demand this of your readership? Either way, strange choice of words.-->
that a scientific product (no matter whether this is a preliminary report or a full research article) should both be understandable by researchers and automatically reproducible by computers with minimal constraints to the researchers' own workflows. <!-- CJ This is ambiguous. The point of "understandable by researchers and automatically reproducible by computers" requires clarification. "Minimal constraints to the workflow" is also not clear. Aren't you providing readers with a workflow? -->

<!-- Which problems are solved by which tool (like in Andreas talk)-->
<!--stolen from: https://brandmaier.github.io/reproducible-data-analysis-materials/KULeuvenQuantPsy2020.html#11 -->
We identified the following common four causes for non-reproducibility: <!-- CJ How did you identify these causes? Is this exhaustive?-->

1.	Multiple inconsistent versions of code and data; for example, the dataset has changed over time because outliers were removed at a later stage, or the code has changed because a bug was removed at some point in time;
2.	Copy-and-paste errors; for example, results are manually copied from a computing environment into a text processor, causing inconsistencies between the reported result and the reproduced result;
3.	Ambiguous order of code execution; for example, with multiple data and code files, it may be unclear which scripts should be executed in what order;
4.	Broken dependencies; for example, a given analysis depends on a software package that might not be available on a different computer or no longer exists.
<!-- CJ 5. Missing steps: Some of the steps are documented (e.g., final analysis), but other steps were conducted manually and not documented (e.g., copy-pasting results from one program to another; reverse coding items on the fly).-->
We have developed a workflow that leverages established tools and practices from software engineering to achieve long-term computational reproducibility of scientific data analyses resting on four pillars that address the aforementioned causes of non-reproducibility [@Peikert2019]: <!-- CJ In fact, this is the central message of your paper: "We have developed this new workflow, based on four pillars." I would suggest mentioning this very clearly in the opening paragraph. The opening paragraph should at least:
1) Introduce the topic area
2) Introduce the problem/knowledge gap
3) Introduce how you will fill this knowledge gap-->

@@

This tutorial follows the recommendations of @Peikert2019 and uses _Git_ for version control, _R Markdown_ for dynamic document creation, _Make_ for dependency tracking, and _Docker_ for software management. <!-- CJ None of these terms have been defined yet-->
The interplay of these four components is shown in Figure \@ref(fig:schematic).
However, which tools you use to implement these concepts is a matter of taste and project requirements, and other choices are possible depending on the context and the degree of reproducibility one aims for [e.g., @vanlissa2020worcs; @turingway2021turing].<!-- CJ But readers do not yet know what these concepts are, nor what tools exist. At this point in the writing, I think you need to take them by the hand and explain. After doing that, you can let them know that there are alternatives.-->
At several points, we suggest other viable alternatives.

@@

This tutorial guides the reader through each step of an open research project with an emphasis on guaranteeing reproducibility from the very first step on.
This paper was designed to help researchers to practically apply the TOP guidelines [except for number 8. which does not apply to single research projects, @nosekPromotingOpenResearch2015; @vanlissa2020worcs].<!-- CJ Is this really the case? Seems like there is little attention to the TOP guidelines, and the present paper is much more widely applicable. Maybe make the general point that workflows can help address formal guidelines for transparency, like TOP and FAIR - and consider citing WORCS for more information. Then explain that your workflow is flexible enough to go beyond--> 
We start by sketching an initial idea in a repository shared with colleagues that potentially collaborate only remotely.<!-- CJ Is this the description of the workflow?-->
We continue with the creation of a concrete data analysis plan, which ideally is already implemented in code, and a dynamic report document that can be preregistered.
Once the empirical data has been collected, the results can be calculated and appear directly in the dynamically generated document, where ideally only the discussion section needs to be added before the whole archive can be permanently stored as a fully reproducible digital artifact in a persistent location, and be assigned a DOI to increase findability.<!--CJ All DOIs are unique, and it is not stored using a DOI-->

@@

Here, we present a workflow that has proven useful for our way of working with a strong focus on Open Science.<!-- CJ What do you mean here? -->
However, not all steps are necessary to achieve reproducibility.
We have marked those steps that can be omitted as "optional" in the section headings.

@@

This tutorial is targeted at scholars with at least intermediate R knowledge<!--CJ This sounds like something that belongs in the beginning of the introduction; it's not part of setup--> and we assume that you have already installed R and RStudio (if not, check the `r link("https://github.com/aaronpeikert/repro-tutorial/blob/main/install.md", "installation guide")`).
To create reproducible research projects in R, we have implemented our workflow in the  [`repro`-package](https://github.com/aaronpeikert/repro)[^repropackage]: <!-- CJ This also seems like something that should be mentioned in the intro; once people are setting up their systems, they should havebeen told what they're setting them up for-->

@@

```r
# -- type this on the R console --
if(!requireNamespace("remotes"))install.packages("remotes")
remotes::install_github("aaronpeikert/repro") # CJ Suggest publishing (at least aminimal working version) of the repro package to CRAN before publishing this paper, to reduce one layer of complexity for users
library("repro")
```

The [`repro`-package](https://github.com/aaronpeikert/repro) contains several helpers to work with the suggested tools for reproducibility.
For example, the package can check if your computer has all the required software packages installed and ready. <!-- CJ Does repro assume that these have already been installed  by hand? -->

@@

If any of these commands find that a given software requirement is not installed or set up properly, you will get a message with detailed instructions (tailored to your operating system) on how to set up your computer.<!-- CJ I think you should explain your philosophy that the package provides additional tutorial instructions depending on the user's situation before diving into the actual tutorial. I foresee that people are going to be puzzled when the tutorial steps present them with additional mini tutorials. Explain in the introduction what the problem is (users need to install andfamiliarize themselves with many different software solutions) and how you solved it (you wrote a package that tells users what dependencies they need to install and how -->
Please make sure that all three commands pass before you continue with the tutorial.
This process is only required once per computer and does not need to be repeated for each project.

# Planning Phase <!-- CJ This reminds me of the WORCS phases, which is fine, but it's the only header that does remind me of these phases. You've not introduced a breakdown of the research process into phases anywhere. Moreover, the text below does not really relate to "planning"; it goes back to reasons for reproducibility, and then an explanation of technical tools (Rmarkdown and Git), neither of which relate to planning! -->

<!-- researcher should begin early to enjoy most benefits -->
Reproducibility is invaluable for effective collaboration---including with your "past self".
While you might be tempted to consider reproducibility only when you about to finish a project, upfront investments pay off through your increased productivity.
Therefore, we suggest starting early, ideally from the moment you decide to pursue a project to incorporate tools to help you achieve reproducibility gradually.
The first step towards reproducibility is to bundle all required files in one folder.
This way, you never lose anything, and you can easily share the files without missing anything.
<!-- Hands-on: Introducing RProjects-->
RStudio's _R Projects_ facilitate this concept of a project folder.
We recomend the [`here`](https://github.com/r-lib/here)[^here] package [@R-here] to refer to files, because it works consistently across different operating systems, and between R scripts and [R Markdown].
The `repro` package offers an R Studio template, which sets up a file structure that follows best practices and conventions for placing scripts and data [@rextensions].
To create one, click on:

@@

<!--Keep notes.-->
 A great tool to capture ideas or meeting notes is Markdown.
 Markdown is a lightweight text format that is very close to plain text with a minimal subset of reserved symbols for formatting instructions.
 This way, Markup does not need any specialized software for editing, it is highly fool-proof (unlike for example LaTeX) and can be ported to various document formats, such as HTML Websites, a Microsoft Word document, a typeset PDF file (for example, via LaTeX journal templates), or a Powerpoint presentation.
We suggest to use Markdown for everything, starting from simple sketches of your ideas to your scientific manuscripts[@R-rticles] and presentations[@revealjs]---and even your CV [@vitae].
To create a Markdown document, click on:

@@

We will later see how this simplicity enables us to create many different document formats (i.e. Word, PDF, HTML) and incorporate code (i.e. R, Python, Julia).

@@

Another advantage of Markdown is that because of its likeness to plain text, you can easily version-control it with Git and leverage Gits features for tracking, displaying, and merging sequential and concurrent changes.
You may be familiar with Microsoft Words' "Track Changes"-Feature.
Version control is similar in its basic idea but more potent in its features.
Instead of tracking only one file, you can keep track of the whole project directory, and instead of losing all changes when you agree to them, the entire history is preserved transparently.
For example, this paper has been going through `r system2("git", c("rev-list",  "--count",  "HEAD"), stdout = TRUE)` `r link("https://github.com/aaronpeikert/repro-tutorial/commits/main", "iterations")`.
To activate Git in a given project, you can call:
<!-- Hands-on: Introduce Git -->

@@

And you could commit it in Git.
For convenience, we use the [`gert`-package](https://github.com/r-lib/gert) [@R-gert], which wraps most git commands into R functions.
Alternatively, we suggest to either work directly in the terminal (for example, RStudio offers a command shell with various options accessible in the Menu Tools → Terminal), or work using the Git pane in RStudio that offers buttons for basic operations.
<!--I am leaning towards doing everything in R, not sure though-->
<!--For Git we maybe should use RStudio's Git pane?-->

To commit your first changes to the project, start with staging all files to be included in the commit using `git_add()`.
Here, we stage our idea collection in the file `idea.md` and then commit it to our local repository with a meaningful commit message that will later help us keep track of all the changes over time.

@@

Now assume that after discussing with your colleagues, you settle onto a final analysis strategy using latent variable models with tests for measurement invariance because power is greater and you want to exclude bias in measurement as possible confounder [@flake2020].
This results in changes to your notes as follows:

@@

And GitHub can show you what has changed, like in Figure \@ref(fig:idea-change).
This detection of what has changed works on a line-by-line basis.
We recommend therefore to keep each sentence in a Markdown on its own line to generate clean difference views.
GitHub is, in its essence, a web interface to Git, and you may learn more about how to use it under the section on [GitHub].

@@

<!--I am troubled by how we should recommend to learn Git-->
Git can be challenging to learn, because it requires a rather complex mental model of maintaining potentially differing versions between different repositories (typically one central repository and one local repository per each author while each repository may have different branches).
However, there is a subsets of commands which we present here and in the section on [GitHub] (commit, push, pull) which enable you to use Git for simple version control.
There are many tutorials on learning Git and @vuorreCuratingResearchAssets2018 provide a good starting point.
However Git is designed for collaboration, we therefore recommend finding a partner to attend an online lecture or workshop to learn the ins and outs of Git.

@@

Monte Carlo simulations are a crucial tool to investigate properties of a statistical model and they are routinely employed to develop or evaluate statistical models.
For example, @maccallum1999sample used Monte Carlo simulations to investigate optimal sample size for exploratory factor analysis, or @curran1996robustness studied the robustness of the $\chi^2$ test statistic under non-normal data.

While rather uncommon for an empirical research project, we argue that simulating data offers various benefits in the planning phase of a study.
First, you have to address and could plan for data analytic problems on a conceptual level before you made the considerable effort to acquire data [@axelrodAdvancingArtSimulation1997].
Second, if you only simulate a single dataset, you can perform a simple technical check, that is the analysis software outputs parameter estimates [@braiekTestingMachineLearning2020], e.g. when the simulated data contains missings.
Third, if you perform a Monte Carlo simulation, you may evaluate how the data analysis copes with expected data complications, e.g. non-normal data [@harrisonIntroductionMonteCarlo2010; @raychaudhuriIntroductionMonteCarlo2008].
Fourth, you can plan your resources efficiently, e.g. determine required sample size to achieve certain precision or power [@brandmaier2018precision].

A Monte Carlo simulation affords you an ideal planning opportunity.
We realize that this comes at an expensive but believe the reduction in the risk that the data is not sufficient to answer the research questions offsets the required effort.
This advantage is especially pronounced when you plan to preregister your study.
In fact, we argue that a Monte Carlo simulation can combine the analysis, sample size planning and preregistration (see [Preregistration as Code].

@@

Typically, it is recommended to choose conservative values in the study planning phase [@brandmaier2018precision].
This way, we make sure that our analytic strategy is viable even in non-optimal circumstances, for example if the measurement instrument works less well then expected or the population characteristics are more different than expected.
As a heuristic guess, we assume that the factor loadings are 30% lower than those reported by @Jones2013 and that the standardized mean difference is only 0.2.
These assumption can be simply translated into [`lavaan` [@R-lavaan]](https://lavaan.ugent.be)[^lavaan] model syntax:

@@

Data simulation is particularly easy in lavaan syntax using the function `simulateData`.
More complicated simulations (for example, including missing data simulation) are possible with other packages, e.g., simsem [@simsem], faux [@faux], or simstudy [@goldfeldSimstudyIlluminatingResearch2020].
The following code simulates data from the population model `model_truth` with 1000 cases in each group.

@@

We propose the following procedure for analyzing the data and dealing with possible violations of strong measurement invariance. 
After fitting the model with strong measurement invariance [@flake2020], we automatically free equality constraints, first on loadings, and then on intercepts based on the Lagrange Multiplier test.
The model is iteratively refit and improved until at most three loadings, or three intercepts are freed, or the Lagrange Multiplier test is not significant for the constraints on loadings or intercepts.
While reconsidering our modeling assumptions, it is also unlikely that the data are perfectly normally distributed.
First, we have rating scale items and thus our observations are categorical.
Second, @Jones2013 reported means not in the middle of the scale, thus suggesting some skewness to the items.
For simplicity of our illustration, we do not simulate these likely data problems (but doing so would undoubtedly make the simulation more realistic).

@@

```{r}
generate_data(1000) %>% 
  planed_analysis() %>% 
  extract_results()
```

@@

Preregistration is the specification of a research plan in advance of data analysis.
The goal of preregistration is transparency and a clear-cut divide into exploration and confirmation.
Thus, it serves as a tool that may help to increase the credibility of empirical results.
Without getting into too much detail of the meta-scientific arguments for preregistration, we want to note two advantages [@nosekPreregistrationHardWorthwhile2019].
First, a preregistration is an opportunity to plan a study carefully.
Gathering empirical data requires many resources, and better planning increases the chances that these efforts are worthwhile.
For us, a good preregistration is the same as a good plan; the only difference is that a preregistration is made public beforehand.

The second advantage is transparency.
A preregistration offers the interested reader more insight into the research process than a paper alone could.
@szollosi_is_2020 argue that preregistration can not fulfil its promise to reduce the false discovery rate of science if we allow deviating from them.
While such an argument has some merits, we believe that often transparency outweighs these concerns [@nosekPreregistrationHardWorthwhile2019].
Deviation from a preregistration is still possible.
If researchers deviate from their preregistration, they probably have good reason to do so, which means they have learned something from the process of conducting the study, and any deviation will simply be explicitly marked as such.
A preregistration, together with version control, allows their readers to inform themselves about these lessons learned.

>>>>

<!-- define replicability and then... 
 define reproducibility -->
Even worse, researchers might often not even be able to achieve reproducibility---defined as the ability to obtain identical results from the *same* data with the *same* computer code.
Over the past decades, computational statistical methods have radically changed the ability of researchers from all disciplines to process and analyze data with complex statistical models.
With these advances came challenges that contribute to broader concerns of irreproducibility in the published literature, among them the lack of exact and unambiguous documentation of computational methods and each computational step taken.
With computationally intensive data analyses, access to the steps taken to process data and generate findings is as important as access to the data themselves [@vanlissa2020worcs].
Only with access to both data and procedures can we guarantee full computational reproducibility, meaning that the creations emanating from a given data analysis (a statistical result or an entire manuscript describing the results) can be exactly reproduced at any time in the future, by any person, and on any computer.

In fact, the research community has long accepted reproducibility as an important element of "good scientific practice." <!-- examples missing -->
However, ensuring reproducibility of computational analyses is still tedious and difficult, and there are still no widely accepted standards that can guide researchers when setting up their data analyses.
Even though transparency has increased across scholarly disciplines (that is, data and methods are increasingly openly shared), most of these open repositories do not provide sufficient information to reproduce relevant computational and statistical results.
For example, @hardwicke2018 attempted to replicate open materials in the journal Cognition.
Out of 35 published articles, results of 22 articles could be reproduced but in 11 of these cases, assistance from the original authors was required.
For 13 articles, at least one outcome could not be reproduced —-- even with the original authors' assistance.
@obels2020 showed that in 62 Registered Reports, 41 had data available, and 37 had analysis scripts available.
The authors could execute only 31 of the scripts without error and were able to reproduce the results of only 21 articles (within a reasonable period of time).
Thus, there is a dire need to establish standards for reproducible workflows for scientific rigor.

From our personal experience, the lack of a proper incentive structure and the dreary perspective of having to spend several extra hours if not days to properly set of a code repository to become reproducible, makes many scholars skip this extra step.
If reproduction would require merely minutes instead of hours, it could greatly facilitate collaboration within and across research projects.
<!-- Guiding principle: spending machine compute time instead of human research time -->
To achieve this boost in productivity, we must place the burden of reproducibility upon computers instead of the researchers.
To this end, we demand that a scientific product (no matter whether this is a preliminary report or a full research article) should both be understandable by researchers and automatically reproducible by computers with minimal constraints to the researchers' own workflows.

<!-- Which problems are solved by which tool (like in Andreas talk)-->
<!--stolen from: https://brandmaier.github.io/reproducible-data-analysis-materials/KULeuvenQuantPsy2020.html#11 -->
We identified the following common four causes for non-reproducibility:

1.	Multiple inconsistent versions of code and data; for example, the dataset has changed over time because outliers were removed at a later stage, or the code has changed because a bug was removed at some point in time;
2.	Copy-and-paste errors; for example, results are manually copied from a computing environment into a text processor, causing inconsistencies between the reported result and the reproduced result;
3.	Ambiguous order of code execution; for example, with multiple data and code files, it may be unclear which scripts should be executed in what order;
4.	Broken dependencies; for example, a given analysis depends on a software package that might not be available on a different computer or no longer exists.

We have developed a workflow that leverages established tools and practices from software engineering to achieve long-term computational reproducibility of scientific data analyses resting on four pillars that address the aforementioned causes of non-reproducibility [@Peikert2019]:

@@

This tutorial follows the recommendations of @Peikert2019 and uses _Git_ for version control, _R Markdown_ for dynamic document creation, _Make_ for dependency tracking, and _Docker_ for software management.
The interplay of these four components is shown in Figure \@ref(fig:schematic).
However, which tools you use to implement these concepts is a matter of taste and project requirements, and other choices are possible depending on the context and the degree of reproducibility one aims for [e.g., @vanlissa2020worcs; @turingway2021turing].
At several points, we suggest other viable alternatives.

@@

This tutorial guides the reader through each step of an open research project with an emphasis on guaranteeing reproducibility from the very first step on.
This paper was designed to help researchers to practically apply the TOP guidelines [except for number 8. which does not apply to single research projects, @nosekPromotingOpenResearch2015; @vanlissa2020worcs].
We start by sketching an initial idea in a repository shared with colleagues that potentially collaborate only remotely.
We continue with the creation of a concrete data analysis plan, which ideally is already implemented in code, and a dynamic report document that can be preregistered.
Once the empirical data has been collected, the results can be calculated and appear directly in the dynamically generated document, where ideally only the discussion section needs to be added before the whole archive can be permanently stored as a fully reproducible digital artifact using a unique DOI in a persistent location.

@@

Here, we present a workflow that has proven useful for our way of working with a strong focus on Open Science.
However, not all steps are necessary to achieve reproducibility.
We have marked those steps that can be omitted as "optional" in the section headings.

@@

This tutorial is targeted at scholars with at least intermediate R knowledge and we assume that you have already installed R and RStudio (if not, check the `r link("https://github.com/aaronpeikert/repro-tutorial/blob/main/install.md", "installation guide")`).
To create reproducible research projects in R, we have implemented our workflow in the  [`repro`-package](https://github.com/aaronpeikert/repro)[^repropackage]:

@@

```r
# -- type this on the R console --
if(!requireNamespace("remotes"))install.packages("remotes")
remotes::install_github("aaronpeikert/repro")
library("repro")
```

The [`repro`-package](https://github.com/aaronpeikert/repro) contains several helpers to work with the suggested tools for reproducibility.
For example, the package can check if your computer has all the required software packages installed and ready.

@@

If any of these commands find that a given software requirement is not installed or set up properly, you will get a message with detailed instructions (tailored to your operating system) on how to set up your computer.
Please make sure that all three commands pass before you continue with the tutorial.
This process is only required once per computer and does not need to be repeated for each project.

# Planning Phase

<!-- researcher should begin early to enjoy most benefits -->
Reproducibility is invaluable for effective collaboration---including with your "past self".
While you might be tempted to consider reproducibility only when you about to finish a project, upfront investments pay off through your increased productivity.
Therefore, we suggest starting early, ideally from the moment you decide to pursue a project to incorporate tools to help you achieve reproducibility gradually.<!--CJ The three preceding sentences belong in the introduction; this tutorial part should be more applied, less conceptual-->
The first step towards reproducibility is to bundle all required files in one folder.
This way, you never lose anything, and you can easily share the files without missing anything.
<!-- Hands-on: Introducing RProjects-->
RStudio's _R Projects_ facilitate this concept of a project folder.
We recomend the [`here`](https://github.com/r-lib/here)[^here] package [@R-here] to refer to files, because it works consistently across different operating systems, and between R scripts and [R Markdown].
The `repro` package offers an R Studio template, which sets up a file structure that follows best practices and conventions for placing scripts and data [@rextensions].
To create one, click on:

@@

<!--Keep notes.-->
 A great tool to capture ideas or meeting notes is Markdown.
 Markdown is a lightweight text format that is very close to plain text with a minimal subset of reserved symbols for formatting instructions.
 This way, Markup<!-- CJ Up or down?--> does not need any specialized software for editing, it is highly fool-proof (unlike for example LaTeX) and can be ported to various document formats, such as HTML Websites, a Microsoft Word document, a typeset PDF file (for example, via LaTeX journal templates), or a Powerpoint presentation.
We suggest to use Markdown for everything, starting from simple sketches of your ideas to your scientific manuscripts[@R-rticles] and presentations[@revealjs]---and even your CV [@vitae].
To create a Markdown document, click on:

@@

We will later see how this simplicity enables us to create many different document formats (i.e. Word, PDF, HTML) and incorporate code in different languages (i.e. R, Python, Julia).

@@

Another advantage of Markdown is that because of its likeness to plain text<!-- CJ This will not make sense to someone who does not yet know how git works and why plain text is preferred, i.e., your target audience-->,
you can easily version-control it with Git and leverage Gits features for tracking, displaying, and merging sequential and concurrent changes.
You may be familiar with Microsoft Words' "Track Changes"-Feature.
Version control <!-- CJ You're now introducing version control after using it in a sentence (preceding). That's too late. Moreover, as the paragraph is labeled "Git", I feel that you should explain git, not version control. Also... shouldn't tools be introduced in the introduction, instead of the tutorial? The tutorial should show users how to use tools that have been explained to them in the introduction.--> 
  is similar in its basic idea but more potent in its features.
Instead of tracking only one file, you can keep track of the whole project directory, and instead of losing all changes when you agree to them, the entire history is preserved transparently.
For example, this paper has been going through `r system2("git", c("rev-list",  "--count",  "HEAD"), stdout = TRUE)` `r link("https://github.com/aaronpeikert/repro-tutorial/commits/main", "iterations")`. <!-- CJ Weird flex, readers will only see the number and won't know that it was dynamically generated from a git call. They also won't understand how that number conveys anything about the benefits of git.-->
To activate Git in a given project, you can call:
<!-- Hands-on: Introduce Git -->

@@

And you could commit it in Git.<!-- CJ Do people know what a commit is yet?-->
For convenience, we use the [`gert`-package](https://github.com/r-lib/gert) [@R-gert], which wraps most git commands into R functions.<!-- CJ Actually, I believe gert is an independent git client - but not 100% sure-->
Alternatively, we suggest to either work directly in the terminal (for example, RStudio offers a command shell with various options accessible in the Menu Tools → Terminal), or work using the Git pane in RStudio that offers buttons for basic operations.
<!--I am leaning towards doing everything in R, not sure though-->
<!--For Git we maybe should use RStudio's Git pane?-->
<!-- CJ No preference yet. I think command line R is convenient, but the R git pane gives a nice overview of new and changed files etc. That would be very instructive to new users. Maybe you can demo how the command line relates to the git pane? I.e., the git pane will be updated when using gert::git_add()-->
To commit your first changes to the project, start with staging all files <!-- CJ do they know what staging is yet? Do they need to know?--> to be included in the commit using `git_add()`.
Here, we stage our idea collection in the file `idea.md` and then commit it to our local repository with a meaningful commit message that will later help us keep track of all the changes over time.

@@

Now assume that after discussing with your colleagues, you decide on a different strategy for the final analysis <!-- CJ I missed what the original plan was-->: using latent variable models with tests for measurement invariance <!--CK consider dropping, it's not essential and confusing to readers who don't know SEM: because power is greater and you want to exclude bias in measurement as possible confounder--> [@flake2020].
This results in changes to your notes as follows:

@@

And GitHub can show you what has changed, like in Figure \@ref(fig:idea-change). <!-- CJ Is the project linked to github yet? Have the changes been pushed? Do readers know what github is yet? -->
This detection of what has changed works on a line-by-line basis. <!-- CJ this should have been explained when you first introduced git -->
We recommend therefore to keep each sentence in a Markdown on its own line to generate clean difference views.
GitHub is, in its essence, a web interface to Git, and you may learn more about how to use it under the section on [GitHub]. <!-- CJ This should have been introduced earlier-->

@@

<!--I am troubled by how we should recommend to learn Git-->
<!-- CJ I think you should avoid teaching people git. You're not teaching them R or how to use RStudio either. Instead, teach readers only the absolute minimum they need to use it. If possible, consider importing the git_update() function into repro, because that will save a lot of explaining in the paper. Do provide a link to a good resource for people who want to learn more; I believe github has tutorial pages.-->
<!-- CJ Also, I feel like most of what is said about git below here should have been in the introduction. Some other snippets (e.g., explaining commit, push and pull) should have been presented before you tell users to make commits. It comes too late here-->
Git can be challenging to learn, because it requires a rather complex mental model of maintaining potentially differing versions between different repositories (typically one central repository and one local repository per each author while each repository may have different branches).
However, there is a subsets of commands which we present here and in the section on [GitHub] (commit, push, pull) which enable you to use Git for simple version control.
There are many tutorials on learning Git and @vuorreCuratingResearchAssets2018 provide a good starting point.
However Git is designed for collaboration, we therefore recommend finding a partner to attend an online lecture or workshop to learn the ins and outs of Git.<!-- CJ I think this is a good sentiment; however, I would (also) provide a link to a good tutorial, and emphasize that all they need to know to get started will be covered in this tutorial, otherwise people get frustrated that they have to go read another tutorial halfway through your tutorial.-->

@@

Monte Carlo simulations <!-- CJ Explain what this is! Or consider using plain language instead.--> are a crucial tool to investigate properties of a statistical model and they are routinely employed to develop or evaluate statistical models.
For example, @maccallum1999sample used Monte Carlo simulations to investigate optimal sample size for exploratory factor analysis, or @curran1996robustness studied the robustness of the $\chi^2$ test statistic under non-normal data.

While rather uncommon for an empirical research project, we argue that simulating data offers various benefits in the planning phase of a study.<!-- CJ I feel that this is a better opening paragraph, because it introduces the concept of simulating data! However, consider that some readers may have no idea of what that means, and might require even more detail.-->
First, you have to address and could plan for data analytic problems on a conceptual level before you made the considerable effort to acquire data [@axelrodAdvancingArtSimulation1997].
Second, if you only simulate a single dataset, you can perform a simple technical check, that is the analysis software outputs parameter estimates [@braiekTestingMachineLearning2020], e.g. when the simulated data contains missings.
Third, if you perform a Monte Carlo simulation, you may evaluate how the data analysis copes with expected data complications, e.g. non-normal data [@harrisonIntroductionMonteCarlo2010; @raychaudhuriIntroductionMonteCarlo2008].
Fourth, you can plan your resources efficiently, e.g. determine required sample size to achieve certain precision or power [@brandmaier2018precision].

A Monte Carlo simulation affords you an ideal planning opportunity.<!-- CJ Put the other monte carlo stuff here, and explain what it is-->
We realize that this comes at an expensive but believe the reduction in the risk that the data is not sufficient to answer the research questions offsets the required effort.<!-- CJ What are you trying to say in this sentence? -->
This advantage is especially pronounced when you plan to preregister your study.
In fact, a Monte Carlo simulation can help plan the analysis in detail, form the basis of power calculation and sample size planning, and can be preregistered integrally (see [Preregistration as Code].<!-- CJ Should this preregistration as code have been introduced earlier? There, you could discuss the notion of simulating data-->

@@

Typically, it is recommended to choose conservative values in the study planning phase [@brandmaier2018precision].
This way, we make sure that our analytic strategy is viable even in non-optimal circumstances, for example if the measurement instrument works less well then expected or the population characteristics are more different than expected.
As a heuristic guess, we assume that the factor loadings are 30% lower than those reported by @Jones2013 and that the standardized mean difference is only 0.2.
These assumption can be simply<!--CJ I wouldn't use this word here. People might find this all quite complicated, and could be disparaged if they read that this should be simple--> translated into [`lavaan` [@R-lavaan]](https://lavaan.ugent.be)[^lavaan] model syntax:

@@

Data simulation is particularly easy in lavaan syntax using the function `simulateData`.
More complicated simulations (for example, including missing data simulation) are possible with other packages, e.g., simsem [@simsem], faux [@faux], or simstudy [@goldfeldSimstudyIlluminatingResearch2020].
The following code simulates data from the population model `model_truth` with 1000 cases in each group. <!-- CJ I'm left wondering whether the example shouldn't simply be a t-test with observed variables. Everybody knows linear models. Lavaan is quite a specialized piece of software, and you might lose a lot of readers when the examples relate to SEM and require understanding of factor loadings, model implied covariance matrices, etc -->

@@

We propose the following procedure for analyzing the data and dealing with possible violations of strong measurement invariance. <!-- CJ Again, mweasurement invariance is probably too technical for an introductory example in a paper about workflows, not SEM-->
After fitting the model with strong measurement invariance [@flake2020], we automatically free equality constraints, first on loadings, and then on intercepts based on the Lagrange Multiplier test. <!-- CJ This is really getting too complex for an example -->
The model is iteratively refit and improved until at most three loadings, or three intercepts are freed, or the Lagrange Multiplier test is not significant for the constraints on loadings or intercepts.
While reconsidering our modeling assumptions, it is also unlikely that the data are perfectly normally distributed.
First, we have rating scale items and thus our observations are categorical.
Second, @Jones2013 reported means not in the middle of the scale, thus suggesting some skewness to the items.
For simplicity of our illustration, we do not simulate these likely data problems (but doing so would undoubtedly make the simulation more realistic).

@@

```{r}
generate_data(1000) %>% 
  planed_analysis() %>% 
  extract_results()
```
<!-- CJ I would just use an example as simple as something like this:
x <- rnorm(100)
y <- .2 + 2.3 * x + rnorm(100)
That's already going to be a big step for many, but hopefully manageable. After grokking that, they can get back to the true point of the paper: Workflows.
-->

@@

Preregistration is the specification of a research plan in advance of data analysis.
The goal of preregistration is transparency and a clear-cut divide into exploration and confirmation.
Thus, it serves as a tool that may help to increase the credibility of empirical results.<!-- CJ For this sentence to make sense, you have to briefly mention the problem with non-preregistered studies: Undisclosed exploration, HARKing, and the file drawer effect-->
Without getting into too much detail of the meta-scientific arguments for preregistration <!-- CJ I think you do need to mention some of those arguments.-->, we want to note two advantages [@nosekPreregistrationHardWorthwhile2019].
First, a preregistration is an opportunity to plan a study carefully.
Gathering empirical data requires many resources, and better planning increases the chances that these efforts are worthwhile.
A preregistration is essentially a detailed research plan; the only difference is that a preregistration is made public <!-- CJ Not necessarily! prereg can be deposited in a private or embargoed repository. The crucial point is that it is time-stamped and indelible, so that future auditors may verify correspondence between the prereg and final analysis. --> beforehand.
